---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SIAModuleIRR2FPR

This package implements a Shiny Item Analysis module for computing binary classification metrics from inter-rater reliability based on Barto코 & Martinkov치 (2022).


## Installation

You can install the development version of `SIAModuleIRR2FPR` like so:

``` r
devtools::install_github("FBartos/SIAModuleIRR2FPR")
```

## Example

The module can be used interactively via the Shiny Item Analysis:


```r
library(ShinyItemAnalysis)
library(SIAModuleIRR2FPR)
run_app()
```

Furthermore, the functions can be also accessed directly from R. 
For example, we use the results reported in Erosheva et. al (2021) to compute the binary classification metrics:
```{r}
library(SIAModuleIRR2FPR)
# use results based on Erosheva et. al (2021)
IRR      <- spearman_brown_formula(0.34, 2.79)
prop_sel <- 0.18

# compute the binary classification metrics
compute_true_positive_rate(IRR, prop_sel)
compute_false_positive_rate(IRR, prop_sel)
compute_false_negative_rate(IRR, prop_sel)
```

and visualize the metrics across the range of possible proportions of selected candidates.
```{r, echo = TRUE}
par(mar=c(4,4,0.1, 0.1))
plot(NA, type = "n", axes = TRUE, bty = "n", xlab = "Proportion selected", ylab = "True positive rate", xlim = c(0, 1), ylim = c(0, 1), las = 1)
x_seq <- seq(0, 1, 0.01)

lines(x_seq, compute_true_positive_rate(IRR = IRR, proportion_selected = x_seq), lwd = 2)
points(prop_sel, compute_true_positive_rate(IRR = IRR, proportion_selected = prop_sel), pch = 16, cex = 1.5)
```

```{r, echo = TRUE}
par(mar=c(4,4,0.1, 0.1))
plot(NA, type = "n", axes = TRUE, bty = "n", xlab = "Proportion selected", ylab = "False positive rate", xlim = c(0, 1), ylim = c(0, 1), las = 1)
x_seq <- seq(0, 1, 0.01)

lines(x_seq, compute_false_positive_rate(IRR = IRR, proportion_selected = x_seq), lwd = 2)
points(prop_sel, compute_false_positive_rate(IRR = IRR, proportion_selected = prop_sel), pch = 16, cex = 1.5)
```

```{r, echo = TRUE}
par(mar=c(4,4,0.1, 0.1))
plot(NA, type = "n", axes = TRUE, bty = "n", xlab = "Proportion selected", ylab = "False negative rate", xlim = c(0, 1), ylim = c(0, 1), las = 1)
x_seq <- seq(0, 1, 0.01)

lines(x_seq, compute_false_negative_rate(IRR = IRR, proportion_selected = x_seq), lwd = 2)
points(prop_sel, compute_false_negative_rate(IRR = IRR, proportion_selected = prop_sel), pch = 16, cex = 1.5)
```

## References
Barto코, F., & Martinkov치, P. (2022). Selecting applicants based on multiple ratings: Using binary classification framework as an alternative to inter-rater reliability. (https://arxiv.org/abs/2207.09101v2)
